Evaluating the Performance and Energy Efficiency of the \textsc{COSMO-ART} Model System

### 2014-05-29 trunk/paper_enahpc14/Sec4:Experimental-results.tex

\begin{figure}[htbf]
  \centering
  \includegraphics[width=0.48\textwidth]{Figs/NRJ_benchmark_Monch.eps}
  \caption{Isola E1 Rack 2 total power of \monch.}
  \label{fig:1}
\end{figure}

@@

Averaged TTS and ETS results  over 10 repetitions of 24h simulation on
\tinto are shown in  Figure~\ref{fig:4}. The corresponding results for
the  averaged total  power are  also shown  in  Table~\ref{tab:1}.  As
expected, the average total power consumption by \cosmoart while using
the \emph{degraded} MPI policy is about  2\,\% less than that consumed by the
\emph{aggressive} one. This is  due to  the reduction of CPU usage (of about 50\,\%) while using  the \emph{degraded} MPI policy, in
contrast with the \emph{aggressive} policy that always yields to 100\,\% of CPU utilization while waiting for an incoming message. From the point of  view of the execution time, there is a
slight reduction  for the \emph{degraded} MPI  policy. One can  expect that the
costs of the context switches produced in the \emph{degraded} MPI policy can lead to
an  increase  of  the   execution  time,  however,  applications  with
extensive computing,  as e.g.  \cosmoart, may show  better performance
with the \emph{degraded} policy. This effect works in  favor with our results
since the energy consumed is also reduced (2\,\%) just by changing the
behavior of the OpenMPI library  to the \emph{degraded} policy, i.e, with the
\texttt{--mca    mpi\_yield\_when\_idle 1}   parameter   set    in   the
\texttt{mpirun} command.

\begin{figure}[htbf]
  \centering
  \includegraphics[width=0.5\textwidth]{Figs/Time_E2S_COSMO-ART-0.eps}
  \caption{Time-to-solution and  energy-to-solution comparison between
    \pilat and \monch for a 24h simulation.}
  \label{fig:3}
\end{figure}

\begin{figure}[htbf]
  \centering
  \includegraphics[width=0.5\textwidth]{Figs/Time_E2S_COSMO-ART-1.eps}
  \vspace{-1cm}
  \caption{Mean time-to-solution and  energy-to-solution on \tinto for
    a 24h simulation using the  \emph{aggressive} and \emph{degraded} MPI policies. The
    95\,\%  confidence  intervals of  Student's  $t$ distribution  (10
    samples) clearly  indicates an improvement for the \emph{degraded} policy in
    both TTS and ETS.}
  \label{fig:4}
\end{figure}

\begin{figure*}[ht]
  \centering
  \hspace{0.8cm} \scalebox{0.62}{\input{Figs/24hour.pstex_t}}
  \caption{24  hours  simulation power  trace  using  the \emph{aggressive}  and
    \emph{degraded} MPI policies on \tinto.}
  \label{fig:5}
\end{figure*}

>>>>

\begin{figure}[htbf]
  \centering
  \includegraphics[width=0.48\textwidth]{Figs/NRJ_benchmark_Monch.eps}
  \caption{Isola E1 Rack 2 total power consumption of \monch.}
  \label{fig:1}
\end{figure}

@@

Averaged TTS and ETS results  over 10 repetitions of 24-hours simulation on
\tinto are shown in  Figure~\ref{fig:4}. The corresponding results for
the  averaged total  power are  also shown  in  Table~\ref{tab:1}.  As
expected, the average total power consumption by \cosmoart while using
the \emph{degraded} MPI policy is about  2\,\% less than that consumed by the
\emph{aggressive} one. This is  due to  the reduction of CPU usage (of about 50\,\%) while using  the \emph{degraded} MPI policy, in
contrast with the \emph{aggressive} policy that always yields to 100\,\% of CPU utilization while waiting for an incoming message. From the point of  view of the execution time, there is a
slight reduction  for the \emph{degraded} MPI  policy. One can  expect that the
costs of the context switches produced in the \emph{degraded} MPI policy can lead to
an  increase  of  the   execution  time,  however,  applications  with
extensive computing,  as e.g.  \cosmoart, may show  better performance
with the \emph{degraded} policy. This effect works in  favor with our results
since the energy consumed is also reduced (2\,\%) just by changing the
behavior of the OpenMPI library  to the \emph{degraded} policy, i.e, with the
\texttt{--mca    mpi\_yield\_when\_idle 1}   parameter   set    in   the
\texttt{mpirun} command.

\begin{figure}[htbf]
  \centering
  \includegraphics[width=0.5\textwidth]{Figs/Time_E2S_COSMO-ART-0.eps}
  \caption{Time-to-solution and  energy-to-solution comparison between
    \pilat and \monch for a 24-hours simulation.}
  \label{fig:3}
\end{figure}

\begin{figure}[htbf]
  \centering
  \includegraphics[width=0.5\textwidth]{Figs/Time_E2S_COSMO-ART-1.eps}
  \vspace{-1cm}
  \caption{Mean time-to-solution and  energy-to-solution on \tinto for
    a 24-hours simulation using the  \emph{aggressive} and \emph{degraded} MPI policies. The
    95\,\%  confidence  intervals of  Student's  $t$ distribution  (10
    samples) clearly  indicates an improvement for the \emph{degraded} policy in
    both TTS and ETS.}
  \label{fig:4}
\end{figure}

\begin{figure*}[ht]
  \centering
  \hspace{0.8cm} \scalebox{0.62}{\input{Figs/24hour.pstex_t}}
  \caption{24-hours simulation power  trace  using  the \emph{aggressive}  and
    \emph{degraded} MPI policies on \tinto.}
  \label{fig:5}
\end{figure*}
